Dependent Object Types

### 2012-08-31 doc/candidacy/report.tex
ML example

\subsection{A Type-Theoretic Approach to Higher-Order Modules with Sharing}

@@

\subsubsection*{SML Example and Scala Encoding}
TODO

\subsection{Tribe: a simple virtual class calculus}

@@

\subsection{A Nominal Theory of Objects with Dependent Types}

>>>>

\subsection{A Type-Theoretic Approach to Higher-Order Modules with Sharing}\label{sec:homl}

@@

\subsubsection*{Pseudo-SML Example and Scala Encoding}
Consider this example, in a ML-like language implementing the calculus
of the paper. Since modules are first-class, we can \code{flip} a coin
and return a module depending on the outcome:
\begin{lstlisting}
structure XInt = struct
  type T = int
  val v = 3
  val f = negate
end
structure XBool = struct
  type T = bool
  val v = true
  val f = not
end
structure X =
  if flip() then XInt else XBool
\end{lstlisting}
But now, what should be the static type or signature of structure
\code{X}? In ML, in order to make the \code{if} type check, the two
branches must have equal types. In the calculus, the subsumption rule
is used to coerce both types to their least upper bound, represented
by the signature:
\begin{lstlisting}
signature XType = sig
  type T
  val v = T
  val f = T -> T
end
\end{lstlisting}

It is straightforward to encode this example in Scala, with the
correspondence Object = Module, and Object Type = Signature. Indeed,
the ${\nu}Obj$ calculus, which we study in section~\ref{sec:nuObj}
embraces this correspondence, and futher claims: Class = Method =
Functor, as we will see.

\subsection{Tribe: a simple virtual class calculus}\label{sec:tribe}

@@

\subsection{A Nominal Theory of Objects with Dependent Types}\label{sec:nuObj}
